Pillar 1 - Sequential Pattern Mining

### 2019-03-21 Pillar 1 - Sequential Pattern Mining.Rmd
create less verbose code with purrr::pmap

library(tidyverse)
library(arulesSequences)
```

# Set up
We load the environment `data_pillar1` which we saved at the end of the data preparation. It contains the data sets `d_course` and `d_transcript`.
```{r loading data}
load("Output/data_general.RDATA")
load("Output/data_pillar_1.RDATA")
```

```{r helper function}
# helper function
join_d_course     <- function(df) df %>% left_join(select(d_course, - Period), by = c("Course ID"))

paste_ <- function(...) paste(..., sep = "_")
```

```{r d_course_informative}
d_transcript_augmented <- d_transcript %>%

  join_d_course %>%

  # Exclude courses taken by majority of students (uninformative)
  filter(
    Type != "Mandatory",
    ! Letters %in% c("SKI", "PRO", "SAS", "SAH", "SAC")
    )
```

```{r constants}
course_all  <- unique(d_transcript_augmented$`Course ID` )
student_all <- unique(d_transcript_augmented$`Student ID`)
n_students  <- length(student_all)
```

@@

```{r statistics set up}
pass_grade <- 5.5
high_grade <- 6.5
```

```{r provide_statistics}
# helper function
provide_statistics <- function(var, df = d_transcript, high_gr = high_grade, pass_gr = pass_grade, join = TRUE){

  if(join) df <- df %>% join_d_course

@@

# Concentration level
statistics$concentration <- d_transcript %>%
  join_d_course %>%
  gather(
    key = X, 
    value = Concentration, 
    Concentration, `Concentration (additional)`,
    na.rm = TRUE
    ) %>%
  provide_statistics(Concentration, df = ., join = FALSE)

@@

# Creating Transactions and Sequences
For a first exploration of arules, we conceptualise our framework like this:
transaction = student
item = course

## Support

```{r d_support TNT}
d_support <- list()

# Probability of taking / failing / obtaining of low grade a course
d_support$TPH <- d_transcript_augmented %>%

@@

  mutate(
    rate.take = n_distinct(`Student ID`) / n_students,
    rate.fail = mean(Grade < pass_grade),
    rate.low  = mean(Grade < high_grade)
    )
```

```{r d_support G}
d_support$G <- d_transcript_augmented %>%

@@

## Data Preparation

### Take, fail, low grade
```{r d_transaction taken_PF_HL}
d_transactions <- list()

d_transactions$taken_PF_HL <- d_transcript_augmented %>%

@@

### Take / not take, pass / fail / not take
```{r d_transactions T_PF_HL}
d_transactions$T_PF_HL <- d_transactions$taken_PF_HL %>%

@@

### Grade
```{r transactions grade}
d_transactions$G <- d_transactions$taken_PF_HL %>%

  mutate(row_of_origin = TRUE) %>%

  complete(
    nesting(sequenceID, eventID, item, Grade), grade_ceil,
    fill = list(row_of_origin = FALSE) # fill missing row_of_origin with FALSE
    ) %>%

@@

#### Save d_transactions
```{r save d_transaction}
save(d_transactions, file = "Output/transaction_df.RDATA")
```

### Transcript with preceding courses (for SR by hand)
```{r d_transcript_cum, cache = TRUE}
d_transcript_cum <- d_transactions$taken_PF_HL %>%

@@

  # lhs: past courses and courses not taken yet, rhs: current courses
  mutate(
    lhs = list(course_past, course_not_yet) %>% pmap(union),
    rhs = course_current
    )
```

## Transactions and sequences
```{r make_transaction}
make_transaction <- function(data, item){

    group_by(sequenceID) %>%
    summarise(list_item = list(unique(!!item))) %>%
    ungroup %>%

    pull(list_item) %>%
    as("transactions")

```{r make_sequence}
make_sequence <- function(data, item){

  if(item == sym("item_TPF") | item == sym("item_THL")) return("Compute sequences that include courses nto taken yet by hand")

```{r transactions, cache = TRUE}
transactions <- tribble(
  ~ ID   ,  ~ data                   , ~ item,
  "taken", d_transactions$taken_PF_HL, sym("item"),
  "PF"   , d_transactions$taken_PF_HL, sym("item_PF"),
  "HL"   , d_transactions$taken_PF_HL, sym("item_HL"),
  "TPF"  , d_transactions$T_PF_HL    , sym("item_TPF"),
  "THL"  , d_transactions$T_PF_HL    , sym("item_TPF"),
  "G"    , d_transactions$G          , sym("item_g")
  ) %>%

  mutate(
    transactions = list(data, item) %>% pmap(make_transaction),
    sequences    = list(data, item) %>% pmap(make_sequence   )
    )

inspect(head(transactions$transactions[[3]], 10))
inspect(head(transactions$sequences   [[3]], 10))
```

```{r, include = FALSE}
rm(
  high_grade, pass_grade, course_all, student_all, n_students,
  d_transactions, d_support, d_transcript_cum,
  make_transaction, transactions, make_sequence, sequences
  )
```

@@

## Functions

### my_aprior, my_cspade and my_ruleInduction

The function `my_apriori()` applies the apriori algorithm on a set of transactions with the parameters that we have chosen.
```{r my_apriori}
my_apriori <- function(data){

@@

      # include all AR possible
      parameter = list(
        supp   = 0, # min support
        smax   = 1, # max support
        conf   = 0, # min confidence
        minlen = 2, # min length of rule
        maxlen = 2  # max length of rule
        ),

      # no printing during execution
      control = list(
        verbose = FALSE
        )

@@

The function `my_cspade()` applies the cspade algorithm on a set of sequential transactions with the parameters that we have chosen.
```{r my_cspade function}
my_cspade <- function(data){

@@

        # include all such subsequences
        support = 0,   # min suppor
        mingap  = 1,   # min time difference between consecutive element
        maxgap  = 1e4  # max time difference between consecutive element

@@

      control = list(
        verbose = FALSE
        )

The function `my_ruleInduction()` creates rules from the set of frequent sequences detemined by cspade.
```{r my_ruleInduction}
my_ruleInduction <- function(rules){

    ruleInduction(

      # keep all subsequences
      confidence = 0,

@@

### clean_rules
The function `clean_AR()` transforms the rules generated by the function `my_apriori()` into a readable dataframe
```{r function clean_rules}
clean_rules <- function(rules){

@@

    # Exclude rules with no support
    filter(
      support > 0
      ) %>%

    # separate rule
    rename_at(
      vars(matches("rule")),
      function(x) substr(x, 1, 4)
    ) %>%
    mutate(
      rule = str_remove_all(rule, pattern = "[<]|[{]|[}]|[>]")
      ) %>%
    separate(
      rule,
      into = c("lhs", "rhs"),
      sep = " = "
      ) %>%

    # separate lhs and rhs
    separate(
      lhs,
      into    = c("lhs_course", "lhs_outcome"),
      sep     = "_",
      remove  = FALSE,
      convert = TRUE
      ) %>%
    separate(
      rhs,
      into    = c("rhs_course", "rhs_outcome"),
      sep     = "_",
      remove  = FALSE,
      convert = TRUE
      )

@@

### compute_rhs.support
The function `compute_support()` computes the support of the lhs and rhs of the rules.
```{r compute_support}
compute_rhs.support <- function(AR, data_support, type_rule){

  AR %>%

    left_join(
      select(data_support, item, !!enquo(type_rule)),
      by = c("rhs_course" = "item")
      ) %>%
    mutate(
      rhs.support = !!enquo(type_rule)
      )

@@

### compute_conf_lift

```{r}
compute_conf_lift <- function(rules){

@@

  # support (and count) of doing lhs and taking course of rhs
  group_by(
    lhs,
    rhs_course
    ) %>%
    mutate(
      lhs.rhsTake.support = sum(support),
      lhs.rhsTake.count   = lhs.rhsTake.support * n_students
      ) %>%
    ungroup %>%

    mutate(
      confidence = support / lhs.rhsTake.support,
      lift       = confidence / rhs.support
      )

@@

### make_AR and  make_SR (wrapers)

We encapsulate the functions `my_apriori()`, `clean_AR()` and `compute_support()` into the function `make_AR()`.
```{r make_AR}
make_AR <- function(data, data_support, type_rule){

  data %>%
    my_apriori %>%
    clean_rules %>%
    compute_rhs.support(
      data_support = data_support,
      type_rule = !!enquo(type_rule)
      )

We encapsulate the fuctions `my_cpade`, `my_ruleInduction`, and `clean_rules` into `make_SR`
```{r make_SR}
make_SR <- function(data, data_support, type_rule){

  data %>%
    my_cspade %>%
    my_ruleInduction %>%
    clean_rules %>%
    compute_rhs.support(
      data_support = data_support,
      type_rule = !!enquo(type_rule)
      )

## Association Rule
We apply make_AR to get different sets of rules:

### take -> take
```{r AR take, cache = TRUE, warning = FALSE}
AR <- list()

AR$taken <- transactions$taken %>%
  make_AR(
    data_support = d_support$TNT, 
    type_rule = rate.take
    )
```

### fail -> fail
```{r AR fail, cache = TRUE}
AR$PF <- transactions$PF %>%

  make_AR(
    data_support = d_support$PF_HL,
    type_rule = rate.fail
    ) %>%

  compute_conf_lift %>%

  # lhs and rhs must be fail
  filter(
    str_detect(lhs, "fail"),
    str_detect(rhs, "fail")
    )
```

### low grade -> low grade
```{r AR low, cache = TRUE}
AR$HL <- transactions$HL %>%

  make_AR(
    data_support = d_support$PF_HL,
    type_rule = rate.low
    ) %>%

  compute_conf_lift %>%

  # lhs and rhs must be fail, count >= 5
  filter(
    str_detect(lhs, "low"),
    str_detect(rhs, "low")
    )
```

### not -> fail
```{r AR TPF, cache = TRUE}
AR$TPF <- transactions$TPF %>%

  make_AR(
    data_support = d_support$PF_HL, 
    type_rule = rate.fail
    ) %>%

  # Confidence and Lift
  filter(
    str_detect(lhs, "not"),
    str_detect(rhs, "fail|pass") # only keep rhsTake for computing confidence and lift
    ) %>%
  compute_conf_lift %>%

  # rhs must be fail, count >= 5
  filter(
    str_detect(rhs, "fail")
    )
```

### not -> low
```{r AR THL, cache = TRUE}
AR$THL <- transactions$THL %>%

  make_AR(
    data_support = d_support$PF_HL, 
    type_rule = rate.low
    ) %>%

  # only keep lhs is not and rhs is low or high to compute Confidence and Lift
  filter(
    str_detect(lhs, "not"),
    str_detect(rhs, "low|high")
    ) %>%
  compute_conf_lift %>%

  # lhs and rhs must be fail, count >= 5
  filter(
    str_detect(rhs, "low")
    )
```

### grade less than or equal to x -> grade less than or equal to 6

```{r AR grade, cache = TRUE}
AR$G <- transactions$G %>%

  clean_rules %>%

  # rhs.support
  left_join(
    d_support$G,
    by = c("rhs_course" = "item", "rhs_outcome" = "grade_ceil")
    ) %>%
  mutate(
    rhs.support = support.grade
    ) %>%

  # Confidence and lift
  group_by(
    lhs, 
    rhs_course
    ) %>%
  mutate(
    lhs.rhsTake.support = max(support),
    lhs.rhsTake.count   = lhs.rhsTake.support * n_students
    ) %>%
  ungroup %>%

  mutate(
    confidence = support / lhs.rhsTake.support,
    lift       = confidence / rhs.support
    ) %>%

  # Reduce number of rules
  filter(
    # exclude rules with same course on lhs and rhs
    lhs_course != rhs_course,
    # rhs is grade less than or equal to 6
    rhs_outcome <= 6,
    lhs_outcome <= 7
    )
```

## Sequence Rules
We apply make_SR to get different types of sequential rules:

### take -> take
```{r SR taken, cache = TRUE, warning = FALSE}
SR <- list()

SR$taken <- sequences$taken %>%

  make_SR(
    data_support = d_support$TNT, 
    type_rule = rate.take
  )
```

### fail -> fail
```{r SR PF, cache = TRUE}
SR$PF <- sequences$PF %>%

  make_SR(
    data_support = d_support$PF_HL,
    type_rule = rate.fail
  ) %>%

  compute_conf_lift %>%

  # lhs and rhs are fail
  filter(
    str_detect(lhs, "fail"),
    str_detect(rhs, "fail")
    )
```

### low grade -> low grade
```{r SR HL, cache = TRUE}
SR$HL <- sequences$HL %>%

  make_SR(
    data_support = d_support$PF_HL,
    type_rule = rate.low
  ) %>%

  compute_conf_lift %>%

  # lhs and rhs are low
  filter(
    str_detect(lhs, "low"),
    str_detect(rhs, "low")
    )
```

### not -> fail
```{r SR TPF, cache = TRUE}
SR$TPF <- d_transcript_cum %>%

  # rhs
  unnest(
    rhs,
    .drop = FALSE
    ) %>%
  filter(
    str_detect(rhs, "pass|fail")
    ) %>%

  # lhs
  unnest(
    lhs,
    .drop = FALSE
    ) %>%
  filter(
    str_detect(lhs, "not")
    ) %>%

  # rule
  unite(
    col = "rule",
    lhs, rhs,
    sep = " => "
    ) %>%

  # rule support
  count(
    rule
    ) %>%
  mutate(
    support = n / n_students
    ) %>%

  # regular fucntions
  clean_rules %>%

  compute_rhs.support(
    data_support = d_support$PF_HL,
    type_rule    = rate.fail
    ) %>%

  compute_conf_lift %>%

  # lhs not, rhs low
  filter(
    str_detect(rhs, "fail")
    )
```

### not -> low
```{r SR THL, cache = TRUE}
SR$THL <- d_transcript_cum %>%

  # rhs
  unnest(
    rhs,
    .drop = FALSE
    ) %>%
  filter(
    str_detect(rhs, "high|low")
    ) %>%

  # lhs
  unnest(
    lhs,
    .drop = FALSE
    ) %>%
  filter(
    str_detect(lhs, "not")
    ) %>%

  # rule
  unite(
    col = "rule",
    lhs, rhs,
    sep = " => "
    ) %>%

  # rule support
  count(
    rule
    ) %>%
  mutate(
    support = n / n_students
    ) %>%

  # regular fucntions
  clean_rules %>%

  compute_rhs.support(
    data_support = d_support$PF_HL,
    type_rule    = rate.low
    ) %>%

  compute_conf_lift %>%

  # constraints to respect
  filter(
    str_detect(rhs, "low")
    )
```

### grade less than or equal to x -> grade less than or equal to 6
```{r SR G, cache = TRUE}
SR$G <- sequences$G %>%

  my_cspade %>%
  my_ruleInduction %>%
  clean_rules %>%

  # rhs.support
  left_join(
    d_support$G,
    by = c("rhs_course" = "item", "rhs_outcome" = "grade_ceil")
    ) %>%
  mutate(
    rhs.support = support.grade
    ) %>%

  # Confidence & lift
  group_by(
    lhs,
    rhs_course
    ) %>%
  mutate(
    lhs.rhsTake.support = max(support),
    lhs.rhsTake.count   = lhs.rhsTake.support * n_students
    ) %>%
  ungroup %>%

  mutate(
    confidence = support / lhs.rhsTake.support,
    lift       = confidence / rhs.support
    ) %>%

  # Reduce number of rules
  filter(
    # exclude rules with same course on lhs and rhs
    lhs_course != rhs_course,
    # rhs is grade less than or equal to 6
    rhs_outcome <= 6,
    lhs_outcome <= 7
    )
```

## Editing rules
The function edit_rules makes AR easier to read. It keeps only rules that appear more than 5 times, rounds numerical variables to 5 significant digits, and drops aiding columns which were only used for computation in previous stages but add no additional information.
```{r edit_rules}
edit_rules_rulesApp <- function(rules){

@@

    mutate(
      count = support * n_students
      ) %>%

@@

    arrange(
      desc(count)
      )

@@

```{r edit rules}
AR_rulesAPP <- lapply(
  X   = AR,
  FUN = edit_rules_rulesApp
  )

SR_rulesAPP <- lapply(
  X   = SR,
  FUN = edit_rules_rulesApp
  )
```

```{r}
save(
  AR_rulesAPP, SR_rulesAPP,
  file = "App/rules/rules.RDATA"
  )
```

```{r show rules}
print(AR_rulesAPP$THL)
print(SR_rulesAPP$THL)
```

```{r}
edit_rules_RSAPP <- function(rules){

    mutate(
      count = support * n_students
      ) %>%

    filter(
       count      >= 10,
       lift       >= 1,
       confidence >= 0.4
      )

```{r}
AR_RSAPP <- lapply(
  X   = AR,
  FUN = edit_rules_RSAPP
  )

SR_RSAPP <- lapply(
  X   = SR,
  FUN = edit_rules_RSAPP
  )
```

```{r save rules, include = FALSE}
save(
  AR_RSAPP, SR_RSAPP,
  file = "App/Recommender System/rules.RDATA"
  )
```

>>>>

library(tidyverse)
library(arulesSequences)
library(magrittr)
```

TODO: simplify support into one df: var1 = course id, var2 = type, var3 = rate

AR with not taken on lhs is not useful.

# Set up
We load the environment `data_pillar1` which we saved at the end of the data preparation. It contains the data sets `d_course` and `d_transcript`.
```{r loading data}
load("Output/data_pillar_1.RDATA")
```

```{r helper function}
paste_ <- function(...) paste(..., sep = "_")
```

```{r constants}
course_all  <- unique(d_transcript_informative$`Course ID` )
student_all <- unique(d_transcript_informative$`Student ID`)
n_students  <- length(student_all)

pass_grade <- 5.5
high_grade <- 6.5
```

@@

```{r provide_statistics}
# helper function
provide_statistics <- function(var, df = d_transcript_augmented, high_gr = high_grade, pass_gr = pass_grade){

@@

# Concentration level
statistics$concentration <- d_transcript_augmented %>%
  gather(
    key = X, 
    value = Concentration, 
    Concentration, `Concentration (additional)`,
    na.rm = TRUE
    ) %>%
  provide_statistics(Concentration, df = .)

@@

# Support
```{r d_support TNT}
d_support <- list()

# Probability of taking / failing / obtaining of low grade a course
d_support$TPH <- d_transcript_informative %>%

@@

  summarise(
    rate.take = n_distinct(`Student ID`) / n_students,
    rate.fail = mean(Grade < pass_grade),
    rate.low  = mean(Grade < high_grade)
    )
```

```{r d_support G}
d_support$G <- d_transcript_informative %>%

@@

# transactions and sequences
For a first exploration of arules, we conceptualise our framework like this:
transaction = student
item = course

```{r d_transactions}
d_transactions <- list()
```

## taken_PF_HL
```{r taken_PF_HL}
d_transactions$taken_PF_HL <- d_transcript_informative %>%

@@

## T_PF_HL (not taken pass/fail high/low)
```{r T_PF_HL}
d_transactions$T_PF_HL <- d_transactions$taken_PF_HL %>%

@@

## Grade
```{r transactions grade}
d_transactions$G <- d_transactions$taken_PF_HL %>%

  mutate(row_of_origin = TRUE) %>%     # non-missing row_of_origin are TRUE

  complete(
    nesting(sequenceID, eventID, item, Grade), grade_ceil,
    fill = list(row_of_origin = FALSE) # missing row_of_origin are FALSE
    ) %>%

@@

## making transactions and sequence
```{r make_transaction}
make_transaction <- function(data, item){

    group_by(sequenceID) %>%
    summarise(list_item = list(unique(!!item))) %>%
    ungroup %$%

    as(list_item, "transactions")

```{r make_sequence}
make_sequence <- function(ID, data, item){

  if(ID %in% c("TPF", "THL")) return("Compute sequences including courses not taken yet by hand")

```{r data_general}
data_general <- tribble(
  ~ ID   ,  ~ data                   , ~ item         , ~ data_support, ~ var_support    , ~ suffix_lhs , ~ suffix_rhs ,
  "taken", d_transactions$taken_PF_HL, sym("item"    ), d_support$TPH , sym("rate.take" ), NA_character_, NA_character_,
  "PF"   , d_transactions$taken_PF_HL, sym("item_PF" ), d_support$TPH , sym("rate.fail" ), "fail"       , "fail"       ,
  "HL"   , d_transactions$taken_PF_HL, sym("item_HL" ), d_support$TPH , sym("rate.low"  ), "low"        , "low"        ,
  "TPF"  , d_transactions$T_PF_HL    , sym("item_TPF"), d_support$TPH , sym("rate.fail" ), "not"        , "fail"       ,
  "THL"  , d_transactions$T_PF_HL    , sym("item_THL"), d_support$TPH , sym("rate.low"  ), "not"        , "low"        ,   
  "G"    , d_transactions$G          , sym("item_g"  ), d_support$G   , sym("rate.grade"), "_7"         , "_7"
  )
```

```{r transactions sequences}
data_general <- data_general %>%

  mutate(
    transactions = list(    data, item) %>% pmap(make_transaction),
    sequences    = list(ID, data, item) %>% pmap(make_sequence)
    ) %>%

  select(-data) # for memory requirement

arules::inspect(head(data_general$transactions[[3]], 10))
arules::inspect(head(data_general$sequences   [[3]], 10))
```

# Transcript with preceding courses
```{r d_transcript_cum, cache = TRUE}
d_transcript_cum <- d_transactions$taken_PF_HL %>%

@@

  # lhs: past courses and courses not taken yet, rhs: current courses
  mutate(
    lhs = list(course_past, course_not_yet) %>% pmap(union),
    rhs = course_current
    ) %>%

  select(lhs, rhs) # for memory requirement
```

```{r, include = FALSE}
rm(
  high_grade, pass_grade, course_all, student_all,
  make_transaction, make_sequence
  )
```

@@

## Helper functions

```{r}
count_min   <- 1
support_min <- count_min / n_students

confidence_min <- 1e-3
```

```{r separate_lhs}
separate_lhs <- function(df) df %>% separate(col = lhs , into = c("lhs_course", "lhs_outcome"), remove  = FALSE, convert = TRUE)
```

```{r separate_rhs}
separate_rhs <- function(df) df %>% separate(col = rhs , into = c("rhs_course", "rhs_outcome"), remove  = FALSE, convert = TRUE)
```

```{r choose_lhs}
choose_lhs <- function(rules, suffix) rules %>% filter(str_detect(lhs, suffix))
```

```{r choose_rhs}
choose_rhs <- function(rules, suffix) rules %>% filter(str_detect(rhs, suffix))
```

### Aprior, CSPADE and rule induction

The function `my_apriori()` applies the apriori algorithm on a set of transactions with the parameters that we have chosen.
```{r my_apriori}
my_apriori <- function(data, supp_min = support_min, conf_min = confidence_min){

@@

      # include all AR possible
      parameter = list(
        supp   = supp_min, # min support
        smax   = 1, # max support
        conf   = conf_min, # min confidence
        minlen = 2, # min length of rule
        maxlen = 2  # max length of rule
        ),

      # no printing during execution
      control = list(verbose = FALSE)

@@

The function `my_cspade()` applies the cspade algorithm on a set of sequential transactions with the parameters that we have chosen.
```{r my_cspade function}
my_cspade <- function(data, supp_min = support_min){

@@

        # include all such subsequences
        support = supp_min,   # min suppor
        mingap  = 1,   # min time difference between consecutive element
        maxgap  = 1e4  # max time difference between consecutive element

@@

@@

The function `my_ruleInduction()` creates rules from the set of frequent sequences detemined by cspade.
```{r my_ruleInduction}
my_ruleInduction <- function(rules, conf_min = confidence_min){

  rules %>% ruleInduction(confidence = conf_min, control = list(verbose = FALSE))

### Separate rules
The function `clean_AR()` transforms the rules generated by the function `my_apriori()` into a readable dataframe
```{r separate_rule}
separate_rule <- function(rules){

@@

    # separate rule
    rename_at(vars(matches("rule")), ~ substr(., 1, 4)) %>%

    mutate(rule = str_remove_all(rule, pattern = "[<]|[{]|[}]|[>]")) %>%

    separate(col = rule, into = c("lhs", "rhs"), sep = " = ") %>%

    # separate lhs and rhs
    separate_lhs %>%
    separate_rhs

@@

### Compute metrics

```{r}
compute_count <- function(rules) rules %>% mutate(count = support * n_students)
```

```{r compute_rhs.support}
compute_rhs.support <- function(rules, ID, data_support, var_support){

  if(ID == "G") by_var <- c("rhs_course" = "Course ID", "rhs_outcome" = "grade_ceil")
  else          by_var <- c("rhs_course" = "Course ID"                              )

    left_join(data_support, by = by_var) %>%

    mutate(rhs.support = !!enquo(var_support)) %>%

    select(- matches("rate"))

@@

```{r compute_lhs.rhsTake}
compute_lhs.rhsTake <- function(rules, ID){

  if(ID == "G") rules <- rules %>% group_by(lhs, rhs_course) %>% mutate(lhs.rhsTake.support = max(support)) %>% ungroup
  else          rules <- rules %>% group_by(lhs, rhs_course) %>% mutate(lhs.rhsTake.support = sum(support)) %>% ungroup

  rules %>% mutate(lhs.rhsTake.count = lhs.rhsTake.support * n_students)

```{r compute_confidence}
compute_confidence <- function(rules, ID){

  if(ID != "taken") rules <- rules %>% mutate(confidence = support / lhs.rhsTake.support)

  rules

```{r compute_lift}
compute_lift <- function(rules) rules %>% mutate(lift = confidence / rhs.support)
```

```{r compute_metrics}
compute_metrics <- function(rules, ID, data_support, var_support){

  rules %>% # rules with support

    compute_count %>%

    compute_rhs.support(ID = ID, data_support = data_support, var_support = !!enquo(var_support)) %>%

    compute_lhs.rhsTake(ID = ID) %>%

    compute_confidence(ID = ID) %>%

    compute_lift %>%

    arrange(desc(support))

### informative_rules
```{r informative_rules}
informative_rules <- function(rules, ID, suffix_lhs, suffix_rhs){

  if(ID != "taken") rules <- rules %>% choose_lhs(suffix_lhs) %>% choose_rhs(suffix_rhs)

  rules %>% filter(lhs_course != rhs_course)

## make_AR, make_SR (wrapers)
We encapsulate the functions `my_apriori()`, `clean_AR()` and `compute_support()` into the function `make_AR()`.
```{r make_AR_regular}
make_AR <- function(ID, transactions, data_support, var_support, suffix_lhs, suffix_rhs){

  transactions %>%

    separate_rule %>%

    compute_metrics(ID = ID, data_support = data_support, var_support = !!enquo(var_support)) %>%

    informative_rules(ID = ID, suffix_lhs = suffix_lhs, suffix_rhs = suffix_rhs)

We encapsulate the fuctions `my_cpade`, `my_ruleInduction`, and `clean_rules` into `make_SR`
```{r make_SR_regular}
make_SR_regular <- function(sequences){

  sequences %>%

    my_cspade %>%

    my_ruleInduction %>%

    separate_rule

```{r make_SR_TPF_THL}
make_SR_TPF_THL <- function(ID){

  if(ID == "TPF") suffix_rhs_take <- "pass|fail"
  else            suffix_rhs_take <- "low|high"

  d_transcript_cum %>%

    # unnest rhs first for memory requirement

    # rhs
    unnest(rhs, .drop = FALSE) %>% 
    choose_rhs(suffix_rhs_take) %>% # keep both pass & fail, or high & low, to compute support support.lhs_rhsTake

    # lhs
    unnest(lhs, .drop = FALSE) %>% 
    choose_lhs("not") %>%
    separate_lhs %>%

    # rule support
    count(lhs, rhs) %>%
    rename(count = n) %>%
    mutate(support = count / n_students) %>%

    separate_lhs %>%
    separate_rhs

```{r make_SR}
make_SR <- function(ID, sequences, data_support, var_support, suffix_lhs, suffix_rhs){

  if(ID %in% c("TPF", "THL")) sequences <- make_SR_TPF_THL(ID = ID)
  else                        sequences <- make_SR_regular(sequences)

   sequences %>%

    compute_metrics(ID = ID, data_support = data_support, var_support = !!enquo(var_support)) %>%

    informative_rules(ID = ID, suffix_lhs = suffix_lhs, suffix_rhs = suffix_rhs)

## Mine Rules
We apply `make_AR` to get different sets of rules:

```{r make rules}
data_general <- data_general %>%

  mutate(
    AR = list(ID, transactions, data_support, var_support, suffix_lhs, suffix_rhs) %>% pmap(make_AR),
    SR = list(ID, sequences   , data_support, var_support, suffix_lhs, suffix_rhs) %>% pmap(make_SR)
    )
```

```{r gather data_general}
rules_clean <- data_general %>%

  gather(key = type_rule, value = rules, AR, SR) %>%

  select(ID, type_rule, rules)
```

# Editing Rules

The function edit_rules makes AR easier to read. It keeps only rules that appear more than 5 times, rounds numerical variables to 5 significant digits, and drops aiding columns which were only used for computation in previous stages but add no additional information.

## App - Recommender System

```{r edit_RS}
edit_RS <- function(rules){

@@

    filter(
       count      >= 20,
       lift       >  1,
       confidence >= 0.4
       )

@@

```{r rules_RS}
rules_clean <- rules_clean %>% mutate(rules_RS = rules %>% map(edit_RS))
```

## App - Rules

```{r edit_rules}
edit_rules <- function(rules){

@@

@@

    arrange(desc(count))

@@

```{r rules_rules}
rules_clean <- rules_clean %>% mutate(rules_rules = rules %>% map(edit_rules))
```

```{r save rules_clean}
save(rules_clean, file = "App/rules_clean.RDATA")
```

```{r save data_general}
save(data_general, file = "Output/rules.RDATA")
```

```{r print SR}
print(rules_clean$rules_RS[[10]])
```
